A self-consistency check for unitary propagation of Hawking quanta

### 2016-11-05 Draft_BH_shells.tex
minor changes

The black hole information paradox \cite{Haw76a} was sharpened to show a self-inconsistency among the following three widely-believed statements \cite{AMPS}\footnote{Different physicists may believe in some of those more strongly than the others, but very few would have argued against any single statement without the explicit conflict in the information paradox.}:
\begin{itemize}
\item {\bf Unitary evaporation:} A black hole will totally evaporate; the formation and evaporation of a black hole is described by an asymptotic observer by a unitary $S$-matrix, whose size is the exponential of the black hole's Bekenstein entropy.
\item {\bf General relativity:} The collapse-Schwarzschild geometry given by general relativity is a valid description of the spacetime everywhere except for near the singularity.
Therefore, there is no drama while crossing the horizon.
\item {\bf Quantum field theory in curved spacetime:} Away from the singularity, we can apply local quantum field theory (QFT) which describes microscopic steps of evaporation. 
For large black holes, it manifests itself as unitary propagation of every near-horizon mode into every asymptotic Hawking quanta.
\end{itemize}
Basically, Statement Three demands that a near horizon mode is related to an asymptotic Hawking quanta by a unitary transformation, and therefore carries the same qubit of information. 
However, Statement One and Two demand this unique qubit to be maximally entangled with two distinct objects, violating monogamy. 
This conflict has inspired many different proposals to modify one of the above three statements. 
For example, information loss or remnant \cite{Bek94} modifies Statement One; 
firewall \cite{BraPir09,AMPS} or ER=EPR \cite{MalSus13} modifies Statement Two;
various proposals of nonlocal effects near the horizon \cite{Gid12,DodSil15,OsuPag16}, causal patch complementarity \cite{HuiYan13,IlgYan13,LowTho14}, or computational complementarity \cite{HH} modify Statement Three.\footnote{Various versions of complementarity basically claim that QFT breaks down if one applies it to compare quantities which are in-principle not measurable (or difficult to measure) by the same observer.}

>>>>

The black hole information paradox \cite{Haw76a} was sharpened to show a self-inconsistency among the following three widely-believed statements \cite{AMPS}\footnote{Different physicists may believe in some of those more strongly than the others, but very few would have argued against any single statement without the explicit conflict in the information paradox.}:
\begin{itemize}
\item {\bf Unitary evaporation:} A black hole will totally evaporate; the formation and evaporation of a black hole is described by an asymptotic observer by a unitary $S$-matrix, whose size is the exponential of the black hole's Bekenstein entropy.
\item {\bf General relativity:} The collapse-Schwarzschild geometry given by general relativity is a valid description of the spacetime everywhere except for near the singularity.
Therefore, there is no drama while crossing the horizon.
\item {\bf Quantum field theory in curved spacetime:} Away from the singularity, we can apply local quantum field theory (QFT) which describes microscopic steps of evaporation. 
For large black holes, it manifests itself as unitary propagation of every near-horizon mode into every asymptotic Hawking quanta.
\end{itemize}
Basically, Statement Three demands that a near horizon mode is related to an asymptotic Hawking quanta by a unitary transformation, and therefore carries the same qubit of information. 
However, Statement One and Two demand this unique qubit to be maximally entangled with two distinct objects, violating monogamy \cite{Bou13}. 
This conflict has inspired many different proposals to modify one of the above three statements. 
For example, information loss or remnant \cite{Bek94} modifies Statement One; 
firewall \cite{BraPir09,AMPS}, ER=EPR \cite{MalSus13}, pre-Hawking radiation \cite{KawMat13,Ho16}, or some version of the fuzzball \cite{Mat15} modifies Statement Two;
various proposals of nonlocal effects near the horizon \cite{Gid12,DodSil15,OsuPag16}, causal patch complementarity \cite{HuiYan13,IlgYan13,LowTho14}, or computational complementarity \cite{HH} modify Statement Three.\footnote{Various versions of complementarity basically claim that QFT breaks down if one applies it to compare quantities which are in-principle not measurable (or difficult to measure) by the same observer.}
